Spatial Analysis

### 2021-06-09 Scripts/spatial_analisis.Rmd
spread ocean data into taxa files for faster computarion on app

```{r dat_exploded, eval = T, echo = F}

@@

>>>>

```{r dat_exploded, eval = T, echo = F, fig.width = 9}

@@

spp_data <- function(spp){

  name_save <- paste0(my_path("D","Spp/Observation"),"obs_",str_replace(spp[1], " ", "_"),".csv")

ocean_data %>% 
  filter(spp == spp,
       region %in% c("Northeast US Fall" , "Northeast US Spring")
       ) %>% 
  write_csv(., name_save)

spp_list <- ocean_data %>% 
  filter(region %in% regions,
         spp != "NA") %>% 
  pull(spp) %>% 
  unique()

lapply(spp_list, spp_data)
